### 2012-05-09 Rctl/inst/doc/manual.Rnw
[Rctl] More working on the manual

Welcome reader to this tutorial, you'll be thrown into the world of network reconstruction 
using differential correlations. This methodology CTL mapping is not the easiest but the 
results can be of great help unraveling trait to trait interactions in all types of 
eukaryotes. In this tutorial I'll try to use as few difficult concepts as possible. But
some always $sneak$ in.\\
\\
Enjoy this tutorial, and good luck hunting that heritability.\\
Danny Arends\\
\\
PS. Use a text-editor\\
PPS. Use a repository/backup system

@@

Some introduction on the methodology, skip this chapter first (Do come back later) if you 
have a dataset and just want to use the software.

@@

<<echo=TRUE,eval=FALSE>>=
require(qtl)        #load the R/qtl package
data(multitrait)    #load the dataset
ctls <- CTLscan.cross(multitrait, pheno.col=1:2)
@

@@

Explains how to map CTL using the CTLscan and CTLscan.network functions.

@@

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:81 were in condition A / e.g. treatment
#Specify that individuals 82:162 were in condition B / e.g. control
conditions <- c(rep(1,81),rep(2,81))
ctls <- CTLscan(ath.metab$genotypes, ath.metab$phenotypes, conditions=)
@

>>>>

Welcome reader to this tutorial, you'll be thrown into the world of network reconstruction 
using differential correlations. This methodology CTL mapping is not the easiest but the 
results can be of great help unraveling trait to trait interactions in all types of 
eukaryotes. In this tutorial I'll try to use as few difficult concepts as possible. But
some always $sneak$ in.\\
\\
Enjoy this tutorial, and good luck hunting that heritability.\\
Danny Arends\\
\\
PS. Use a good text editor\\
PPS. Use a repository / backup system

@@

Some introduction on the methodology, skip this chapter first (DO come back later) if you 
have a dataset and just want to use the software.

@@

<<echo=TRUE,eval=FALSE>>=
require(qtl)        #Loads the R/qtl package
data(multitrait)    #Loads the dataset
multitrait          #Print basic dataset information
@

@@

Explains how to map CTL using the CTLscan and CTLscan.network functions.
<<echo=TRUE,eval=FALSE>>=
require(ctl)        #Loads the R/ctl package
data(ath.metab)
geno <- ath.metab$genotypes #Short name
traits <- ath.metab$phenotypes #Short name

#Scan all phenotypes for CTLs, using the default options
#NOTE: Could take some time
ctls <- CTLscan(geno,traits)
@

@@

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:81 were in condition A / e.g. treatment
#Specify that individuals 82:162 were in condition B / e.g. control
conditions <- c(rep(1,81),rep(2,81))
ctls <- CTLscan(geno, traits, conditions=conditions)
@
